\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2014-12-03 paper/subdocuments/results.Rnw
gini berechnet für special cases

# Export data to use with Stata
ns1993_94 <- rbind(data.frame(cbind("income" = pooled_i,"group"=0)),data.frame("income" = normal_i,"group"=1))
ns1993_94$group <- factor(ns1993_94$group,labels=c("pooled","normal"))
write.dta(ns1993_94, file="../../data/stata_data/ns1993_94.dta")

@@

>>>>

# Export data to use with Stata
ns1993_94 <- rbind(data.frame(cbind("income" = pooled_i,"group"=0)),data.frame("income" = normal_i,"group"=1))
ns1993_94$group <- factor(ns1993_94$group,labels=c("pooled","normal"))
write.dta(ns1993_94, file="../../data/stata_data/ns1993_94.dta")
# Ginis berechnen
gini_allcases <- gini(ns1993_94$income[ns1993_94$group=="pooled"]); gini_allcases
gini_normal <- gini(ns1993_94$income[ns1993_94$group=="normal"]); gini_normal
round(gini_allcases-gini_normal,3)
# 0.013

@@

#Gini Range
gini_allcases <- gini(ns2010$income[ns1993_94$group=="pooled"]); gini_allcases
gini_normal <- gini(ns2010$income[ns1993_94$group=="normal"]); gini_normal
round(gini_allcases-gini_normal,3)
# 0.025
